---
title: "Data Science Final Project"
Authors: "Malio Mayo"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
editor_options: 
  markdown: 
    wrap: sentence
---

# An Analysis of Movies from 2006-2016

## Team

-   **Malio Mayo**

### Introduction

Movies have been a pivotal part of most people's lives, whether it was a movie you saw as a kid that changed your view on the world, or a movie about a funny dinosaur that just made you laugh.
Everyone loves a good movie, but what about the movie made it so great?

Asking the data these questions:

-   Year with the most releases

-   What movies did the best in this time period?
    Who directed them?

-   What movies did the worst in this time period?
    Who directed them?

-   How does IMDb's rank of the movie for this segment of time compare to the rating?

To answer these questions:

-   Does Genre affect how the movie does?

-   Who (Director) makes the best movies?

-   Who (Director) makes the worst movies?

-   What was the Best rated movie of 2006-2016 based on the data?

-   What was the Worst rated movie of 2006-2016 based on the data?

### Prerequisites

```{r}
library(tidyverse)
library(ggplot2)
library (readr)
```

### Dataset

```{r}

urlfile="https://raw.githubusercontent.com/reisanar/datasets/master/IMDB_movies.csv"

IMDB<-read_csv(url(urlfile))
IMDB
```

### Data Analysis

#### Year with the most releases:

```{r}
IMDB %>%
  group_by(Year)%>%
  summarize(Total = n())%>%
  
ggplot() +
  geom_col(aes(x=Year, y = Total))
```

2016 had the most releases in this decade span of time.

#### Movies with the lowest ratings:

```{r}
IMDB %>%
  na.omit()%>%
  select(Title,Genre,Director,Rating)%>%
  arrange(Rating)%>%
  unique()
```

The worst movie made in the 2006-2016 Decade was Disaster Movie, Directed by Jason Friedberg and received a rating of 1.9.

#### Movies with the Best Ratings:

```{r}
IMDB %>%
  na.omit()%>%
  select(Title,Genre,Director,Rating)%>%
  arrange(desc(Rating))%>%
  unique()
```

The Dark Knight was the highest rated movie in the 2006-2016 Time Span, its Director was Christopher Nolan and received a 9.0 rating.

#### Comparing IMDb's Ranking to the Ratings

```{r}
IMDB %>%
  na.omit()%>%
  select(Title,Rank,Rating)%>%
  arrange((Rank))%>%
  unique()
```

The IMDb ranking system puts Guardians of the Galaxy as the number one movie with a rating of 8.1.

### Answering our Questions

The questions:

-   Does Genre affect how the movie does?

-   Who (Director) makes the best movies?

-   Who (Director) makes the worst movies?

-   What was the Best rated movie of 2006-2016 based on the data?

-   What was the Worst rated movie of 2006-2016 based on the data?

#### Does Genre affect how the movie does?

According to the data, It does.
Most of the movies in the top 20 have at least one of these listed as a genre: Action, Drama or Adventure.
Which leads me to the conclusion that a movie that qualifies as an Action, Drama or Adventure movie will do better at the box office than other movies.

#### Who makes the best movies?

In the top 10 movies listed in the data, Christopher Nolan directed 5 of them.
I think its safe to say that for the 2006-2016 Time Span, Christopher Nolan was the best Director.

#### Who makes the worst movies?

In the worst 50 movies rated in the 2006-2016 period, M.
Night Shyamalan and Rob Cohen made 2 movies in the 50 worst rated movies, I would call that a tie for who made the worst movies in the 2006-2016 period.

#### What was the best rated movie in the 2006-2016 Time Span?

The best rated movie in the 2006-2016 Time Span was The Dark Night, Directed by Christopher Nolan, and was given a rating of 9.0.

#### What was the worst rated movie in the 2006-2016 Time Span?

The worst rated movie in the 2006-2016 Time Span was Disaster Movie, Directed by Jason Friedberg, and was given a rating of 1.9.

### Conclusion

In conclusion, Christopher Nolan makes the best movies and Genre does matter in order for the movie to succeed.
